Cover letter for the original IJRR submission

### 2017-12-12 body/appendix_algo.tex
uniform syntax

At each step, \textsc{GenFullBody} is called with the previous state as a parameter, as well
as a new root configuration. \textsc{GenFullBody} returns a new contact configuration, if it succeeded
in computing a configuration with only one contact switch occurring.
Otherwise, the method \textsc{IntermediateContactState} is called.
It repositions one end effector (either a free limb, or the oldest active contact) towards a new contact position if possible.
This repositioning allows to increase the odds that the contact can be maintained at the next step.
The method \textit{last\_element} returns the last element
of the list, \textit{element} returns the element contained by a list at a given index, and \textit{push\_back} inserts an element at the end of a list.
Algorithm~\ref{alg:pi} gives the pseudo code for \textsc{GenFullBody}.

\begin{algorithm}[!tbp]
\caption{Full body contact generation method} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{\textsc{GenFullBody}}{$pState$,$\mathbf{q}^0$}
		\State $newState \gets create\_state(q0, FreeLimbs(pState))$
		\State /*First try to maintain previous contacts*/
		\State $nConBroken \gets 0$
		\For {\textbf{each} $k$ in $ContactLimbs(pState)$}
			\If {$!$\textsc{MaintainContact}$(pState,\mathbf{q}^0,k)$}
				\State $nConBroken \gets nConBroken +1$
				\If {$nConBroken > 1$}				
					\State \textbf{return} $0$
				\EndIf				
				\State $add\_free\_limb(newState,k)$
			\Else 					
				\State $add\_contact\_limb(newState,k)$
			\EndIf
		\EndFor
		\For {\textbf{each} $k$ in $FreeLimbs(pState)$}
			\If {\textsc{GenerateContact}$(\mathbf{q}^0,k)$}	
				\State $add\_contact\_limb(newState,k)$
				\State \textbf{return} $newState$
			\EndIf
		\EndFor
		\If {\textsc{IsInStaticEquilibrium}$(newState)$}
			\State \textbf{return} $newState$
		\Else
			\State \textbf{return} $0$
		\EndIf
	\EndFunction
\end{algorithmic}
\label{alg:pi}
\end{algorithm}

@@

The method \textsc{IsInStaticEquilibrium} returns whether a given state is in static equilibrium.
$ContactLimbs$ (respectively $FreeLimbs$) returns the list of limbs that are in contact (respectively \textit{not} in contact) at a given state. $add\_contact\_limb$ (respectively $add\_free\_limb$)  marks a limb as in contact (respectively \textit{not} in contact) at a given state.
%~ $add\_contact\_limb(newState,k)$ marks a limb as in contact at a given state.

>>>>

At each step, \textsc{GenFullBody} is called with the previous state as a parameter, as well
as a new root configuration. \textsc{GenFullBody} returns a new contact configuration, if it succeeded
in computing a configuration with only one contact switch occurring.
Otherwise, the method \textsc{IntermediateContactState} is called.
It repositions one end effector (either a free limb, or the oldest active contact) towards a new contact position if possible.
This repositioning allows to increase the odds that the contact can be maintained at the next step.
The method \textit{length} returns the length of a list, \textit{last\_element} returns the last element
of a list, \textit{element} returns the element contained by a list at a given index, and \textit{push\_back} inserts an element at the end of a list.
Algorithm~\ref{alg:pi} gives the pseudo code for \textsc{GenFullBody}.

\begin{algorithm}[!tbp]
\caption{Full body contact generation method} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{\textsc{GenFullBody}}{$pState$,$\mathbf{q}^0$}
		\State $newState \gets CreateState(q0, ContactLimbs(pState))$
		%~ \State /*First try to maintain previous contacts*/
		\State $nConBroken \gets 0$
		\For {\textbf{each} $k$ in $ContactLimbs(pState)$}
			\If {$!$\textsc{MaintainContact}$(pState,\mathbf{q}^0,k)$}
				\State $nConBroken \gets nConBroken +1$
				\If {$nConBroken > 1$}				
					\State \textbf{return} $0$
				\EndIf				
				\State $MarkFree(newState,k)$
			\Else 					
				\State $MarkContact(newState,k)$
			\EndIf
		\EndFor
		\For {\textbf{each} $k$ in $FreeLimbs(pState)$}
			\If {\textsc{GenerateContact}$(\mathbf{q}^0,k)$}	
				\State $MarkContact(newState,k)$
				\State \textbf{return} $newState$
			\EndIf
		\EndFor
		\If {\textsc{IsInStaticEquilibrium}$(newState)$}
			\State \textbf{return} $newState$
		\Else
			\State \textbf{return} $0$
		\EndIf
	\EndFunction
\end{algorithmic}
\label{alg:pi}
\end{algorithm}

@@

The method \textsc{IsInStaticEquilibrium} returns whether a given state is in static equilibrium. $CreateState$ creates a new state, given
a configuration and the list of active contacts.
$ContactLimbs$ (respectively $FreeLimbs$) returns the list of limbs that are in contact (respectively \textit{not} in contact).  $MarkContact$ (respectively $MarkFree$)  marks a limb as in contact (respectively \textit{not} in contact).
%~ $add\_contact\_limb(newState,k)$ marks a limb as in contact at a given state.
